---
title: Tuango - RFM Analysis for Mobile App Push Messaging on the post roll-out data
output: html_document
---

* Name:
* GitLab id:
* GitLab username:

```{r r_setup, include = FALSE}
## initial settings
knitr::opts_chunk$set(
  comment = NA,
  echo = TRUE,
  error = TRUE,
  cache = FALSE,
  message = FALSE,
  dpi = 96,
  warning = FALSE
)

## width to use when printing tables etc.
options(
  width = 250,
  scipen = 100,
  max.print = 5000,
  stringsAsFactors = FALSE
)

## make all required libraries available by loading radiant package if needed
if (!exists("r_environment")) library(radiant)
```

<style>
.table {
  width: auto;
}
ul, ol {
  padding-left: 18px;
}
pre, code, pre code {
  overflow: auto;
  white-space: pre;
  word-wrap: normal;
  background-color: #ffffff;
}
</style>

## Setup

Please complete this Rmarkdown document by answering question 14 in `tuango.pdf` on Dropbox (week4/readings/). The code block below will load the data you will need. Create a Notebook/HTML file with all your results and answers and push both the Rmarkdown and Notebook/HTML file to GitLab when you are done. All results MUST be reproducible (i.e., the TA and I must be able to recreate the Notebook/HTML from the Rmarkdown file without changes or errors).

```{r}
## loading the data. Note that data must be loaded from Dropbox/MGTA455-2019/data
tuango<- readr::read_rds(file.path(radiant.data::find_dropbox(), "MGTA455-2019/data/tuango_post.rds"))
tuango <- tuango %>%
  mutate(rec_iq = radiant.data::xtile(recency, 5))%>%
  mutate(freq_iq = radiant.data::xtile(frequency,5,rev=TRUE))%>%
  mutate(mon_iq = radiant.data::xtile(monetary,5,rev=TRUE))
tuango <- tuango %>%
  mutate(rfm_iq = paste0(rec_iq,freq_iq,mon_iq))
identical(tuango$rfm_iq_pre,tuango$rfm_iq)
tuango <-tuango %>%
  mutate(rec_sq = radiant.data::xtile(recency, 5))%>%
  group_by(rec_sq)%>%
  mutate(freq_sq= radiant.data::xtile(frequency, 5,rev=TRUE))%>%
  ungroup()%>%
  group_by(rec_sq,freq_sq)%>%
  mutate(mon_sq =radiant.data::xtile(monetary, 5,rev=TRUE))%>%
  ungroup()%>%
  mutate(rfm_sq = paste0(rec_sq,freq_sq,mon_sq))

```
```{r}
train_set<- tuango %>%
  filter(training == 1)
test_set <- tuango %>%
  filter(training == 0)
train_set<- train_set%>%
  mutate(buyer = ifelse(buyer == "yes", 1, 0))
test_set<- test_set%>%
  mutate(buyer = ifelse(buyer == "yes", 1, 0))
amount_spent <- train_set %>%
  filter(buyer == 1)
amount_spent<- mean(amount_spent$ordersize)
amount_spent
breakeven_response_rate <- 1.6/(0.5*amount_spent)
breakeven_response_rate
```
```{r}
#offer to all
profit <- (mean(test_set$ordersize)*0.5-1.6)*count(test_set)
ROME<- profit/(count(test_set)*1.6)
profit
ROME
```
```{r}
#question 9
perf_calc <- function(data_train,data_test,column_name){
  select_rfm <- data_train %>%
  group_by_at(column_name)%>%
  mutate(choose_test = mean(buyer)>breakeven_response_rate)%>%
  filter(choose_test == TRUE)%>%
  summarize(n=n())%>%
  select_at(column_name)%>%
  ungroup()
  data_test<- data_test %>%
    mutate(choose_train  = data_test[[column_name]] %in% select_rfm[[column_name]])%>%
    filter(choose_train == TRUE)%>%
    mutate(revenue = ordersize *0.5)
  cost <- count(data_test)*1.6
  profit <- sum(data_test$revenue)-cost
  ROME <-profit/cost
  return(c(cost,profit,ROME))

}
rfm_iq_question9<-perf_calc(train_set,test_set,'rfm_iq')
rfm_sq_question9<-perf_calc(train_set,test_set,'rfm_sq')
rfm_iq_question9
rfm_sq_question9
```
```{r}
#question11
perf_calc2 <- function(data_train,data_test,column_name){
data_train_sub<- data_train%>%
  filter(buyer == 1)%>%
  group_by_at(column_name)%>%
  summarize(size = mean(ordersize))
data_train_sub2<- data_train %>%
  group_by_at(column_name)%>%
  summarize(rate=mean(buyer),n=n())%>%
  right_join(data_train_sub,by = column_name)%>%
  mutate(breakeven_response_rate = 1.6/(size*0.5))%>%
  mutate(choose_train = breakeven_response_rate< rate)%>%
  filter(choose_train == TRUE)
  data_test<- data_test %>%
    mutate(choose_train  = data_test[[column_name]] %in% data_train_sub2[[column_name]])%>%
    filter(choose_train == TRUE)%>%
    mutate(revenue = ordersize *0.5)
  cost <- count(data_test)*1.6
  profit <- sum(data_test$revenue)-cost
  ROME <-profit/cost
  return(c(cost,profit,ROME))
}

rfm_sq_question11<-perf_calc2(train_set,test_set,'rfm_sq')
rfm_sq_question11
```
```{r}
perf_calc3 <- function(data_train,data_test,column_name){
data_train_sub<- data_train%>%
  filter(buyer == 1)%>%
  group_by_at(column_name)%>%
  summarize(size = mean(ordersize))
data_train_sub2<- data_train %>%
  group_by_at(column_name)%>%
  summarize(rate=mean(buyer)-1.64*seprop(buyer),n=n())%>%
  right_join(data_train_sub,by = column_name)%>%
  mutate(breakeven_response_rate = 1.6/(size*0.5))%>%
  mutate(choose_train = breakeven_response_rate< rate)%>%
  filter(choose_train == TRUE)
  data_test<- data_test %>%
    mutate(choose_train  = data_test[[column_name]] %in% data_train_sub2[[column_name]])%>%
    filter(choose_train == TRUE)%>%
    mutate(revenue = ordersize *0.5)
  cost <- count(data_test)*1.6
  profit <- sum(data_test$revenue)-cost
  ROME <-profit/cost
  return(c(cost,profit,ROME))
}

rfm_sq_question12<-perf_calc3(train_set,test_set,'rfm_sq')
rfm_iq_question12<-perf_calc3(train_set,test_set,'rfm_iq')
rfm_iq_question12
rfm_sq_question12

```

```{r}
library(dplyr)
bar_profit <- data.frame(name=c('iq_9','sq_9','sq_11','iq_12','sq_12'),profit=c(as.numeric(rfm_iq_question9[2]),as.numeric(rfm_sq_question9[2]),as.numeric(rfm_sq_question11[2]),as.numeric(rfm_iq_question12[2]),as.numeric(rfm_sq_question12[2])) )%>%
  ggplot(aes(x=name,y=profit))+geom_bar(stat = 'identity')+coord_cartesian(ylim=c(300000,500000))
bar_ROME <- data.frame(name=c('iq_9','sq_9','sq_11','iq_12','sq_12'),ROME=c(as.numeric(rfm_iq_question9[3]),as.numeric(rfm_sq_question9[3]),as.numeric(rfm_sq_question11[3]),as.numeric(rfm_iq_question12[3]),as.numeric(rfm_sq_question12[3]))) %>%
  ggplot(aes(x=name,y=ROME))+geom_bar(stat = 'identity')+coord_cartesian(ylim=c(1.5,3.5))
bar_profit
bar_ROME   
```


