---
title: Tuango - RFM Analysis for Mobile App Push Messaging
output: html_document
---

* Name:
* GitLab id:
* GitLab username:

```{r r_setup, include = FALSE}
## initial settings
knitr::opts_chunk$set(
  comment = NA,
  echo = TRUE,
  error = TRUE,
  cache = FALSE,
  message = FALSE,
  dpi = 96,
  warning = FALSE
)

## width to use when printing tables etc.
options(
  width = 250,
  scipen = 100,
  max.print = 5000,
  stringsAsFactors = FALSE
)

## make all required libraries available by loading radiant package if needed
if (!exists("r_environment")) library(radiant)
```

<style>
.table {
  width: auto;
}
ul, ol {
  padding-left: 18px;
}
pre, code, pre code {
  overflow: auto;
  white-space: pre;
  word-wrap: normal;
  background-color: #ffffff;
}
</style>

## Setup

Please complete this R-markdown document by answering the questions in `tuango.pdf` on Dropbox (week4/readings/). The code block below will load the data you will need for this first Rmarkdown file. Create a Notebook/HTML file with all your results and answers and push both the Rmarkdown and Notebook/HTML file to GitLab when you are done. All results MUST be reproducible (i.e., the TA and I must be able to recreate the Notebook/HTML from the R-markdown file without changes or errors).

```{r}
## loading the data. Note that data must be loaded from Dropbox/MGTA455-2019/data
library(dplyr)
tuango <- readr::read_rds(file.path(radiant.data::find_dropbox(), "MGTA455-2019/data/tuango.rds"))
buyer<- tuango %>%
  group_by(buyer)%>%
  summarize(n=n())
buyer_percentage <-as.numeric(buyer[1,2]/(buyer[2,2]+buyer[1,2]))
buyer_percentage
```
Question 1 0.0298

```{r}
amount_spent <- tuango %>%
  filter(buyer == 'yes')
amount_spent<- mean(amount_spent$ordersize)
amount_spent
```
Question2  202.1288
```{r}
tuango <- tuango %>%
  mutate(rec_iq = radiant.data::xtile(recency, 5))%>%
  mutate(freq_iq = radiant.data::xtile(frequency,5,rev=TRUE))%>%
  mutate(mon_iq = radiant.data::xtile(monetary,5,rev=TRUE))
```

```{r}
rec1 <- tuango %>%
  mutate(buyer = as.numeric(buyer))%>%
  filter(buyer == 1)%>%
  group_by(rec_iq)%>%
  summarize(n= sum(buyer))
plot1 <- tuango%>%
  group_by(rec_iq)%>%
  summarize(n2 = n())%>%
  right_join(rec1,by='rec_iq')%>%
  mutate(percentage= n/n2)%>%
  ggplot(aes(rec_iq,percentage))+geom_bar(stat='identity')
freq1 <- tuango %>%
  mutate(buyer = as.numeric(buyer))%>%
  filter(buyer == 1)%>%
  group_by(freq_iq)%>%
  summarize(n= sum(buyer))
plot2 <- tuango%>%
  group_by(freq_iq)%>%
  summarize(n2 = n())%>%
  right_join(freq1,by='freq_iq')%>%
  mutate(percentage= n/n2)%>%
  ggplot(aes(freq_iq,percentage))+geom_bar(stat='identity')
mon1 <- tuango %>%
  mutate(buyer = as.numeric(buyer))%>%
  filter(buyer == 1)%>%
  group_by(mon_iq)%>%
  summarize(n= sum(buyer))
plot3 <- tuango%>%
  group_by(mon_iq)%>%
  summarize(n2 = n())%>%
  right_join(mon1,by='mon_iq')%>%
  mutate(percentage= n/n2)%>%
  ggplot(aes(mon_iq,percentage))+geom_bar(stat='identity')
show(plot1)
show(plot2)
show(plot3)
```

```{r}
rec2 <- tuango %>%
  mutate(buyer = as.numeric(buyer))%>%
  filter(buyer == 1)%>%
  group_by(rec_iq)%>%
  summarize(ordersize= mean(ordersize))
rec2 %>%
  ggplot(aes(rec_iq,ordersize))+geom_bar(stat='identity')
rec2 %>%
  ggplot(aes(rec_iq,ordersize-min(ordersize)))+geom_bar(stat='identity')
freq2 <- tuango %>%
  mutate(buyer = as.numeric(buyer))%>%
  filter(buyer == 1)%>%
  group_by(freq_iq)%>%
  summarize(ordersize= mean(ordersize))%>%
  ggplot(aes(freq_iq,ordersize))+geom_bar(stat='identity')
mon2 <- tuango %>%
  mutate(buyer = as.numeric(buyer))%>%
  filter(buyer == 1)%>%
  group_by(mon_iq)%>%
  summarize(ordersize= mean(ordersize))%>%
  ggplot(aes(mon_iq,ordersize))+geom_bar(stat='identity')
show(freq2)
show(mon2)
```
Question 6 After we quintiles the RFM factors,We find that higher rec level ,frequency level and higher monetary level lead to higher response rate.But for ordersize ,there is no significant tread to prove that rec level, frequency level and monetary will influence ordersize level.
## Question answers
```{r}
tuango <- tuango %>%
  mutate(rfm_iq = paste0(rec_iq,freq_iq,mon_iq))
identical(tuango$rfm_iq_pre,tuango$rfm_iq)
tuango <-tuango %>%
  mutate(rec_sq = radiant.data::xtile(recency, 5))%>%
  group_by(rec_sq)%>%
  mutate(freq_sq= radiant.data::xtile(frequency, 5,rev=TRUE))%>%
  ungroup()%>%
  group_by(rec_sq,freq_sq)%>%
  mutate(mon_sq =radiant.data::xtile(monetary, 5,rev=TRUE))%>%
  ungroup()%>%
  mutate(rfm_sq = paste0(rec_sq,freq_sq,mon_sq))
```
```{r}
breakeven_response_rate <- 1.6/(0.5*amount_spent)
breakeven_response_rate
```
Question7 breakeven response rate is 0.0158
```{r}
profit <- (mean(tuango$ordersize)*0.5-1.6)*250902
ROME<- profit/(250902*1.6)
profit
ROME
```
Quesiton8
Profit is 354417 and ROME is 88.29% 
```{r}
tuango<- tuango%>%
  mutate(buyer = ifelse(buyer == "yes", 1, 0))
```

```{r}
perf_calc <- function(data,column_name){
  data <- data %>%
  group_by_at(column_name)%>%
  mutate(choose_test = mean(buyer)>breakeven_response_rate)%>%
  ungroup()
  perc_choose <- mean(data$choose_test)
  number_choose <- perc_choose *250902
  dat <-filter(data,choose_test ==TRUE)
  rep_rate<-mean(dat$buyer== 1)
  nr_resp <-number_choose*rep_rate
  cost1<-1.6*number_choose
  profit1<-amount_spent*0.5*nr_resp-cost1
  ROME1 <-profit1/cost1
  return(c(cost1,profit1,ROME1))
}
iq<-perf_calc(tuango,'rfm_iq')
sq<-perf_calc(tuango,'rfm_sq')
 
iq
sq
profit_iq <- iq[2]
ROME_iq <- iq[3]
profit_sq <-sq[2]
ROME_sq <- sq[3]
```

Qusetion9 
For iq ,profit is 447457.3 and ROME is 1.8844
For sq ,profit is 451112.5 and ROME is 1.9370

```{r}
plot_iq<- tuango %>% 
  group_by(rfm_iq)%>%
  summarize(n= mean(buyer))%>%
  ggplot(aes(x=rfm_iq,y=n))+geom_bar(stat='identity')+geom_hline(aes(yintercept=breakeven_response_rate))+ coord_flip()+theme(axis.text.y = element_text(face="bold", color="black", size=5))
plot_sq<- tuango %>% 
  group_by(rfm_sq)%>%
  summarize(n= mean(buyer))%>%
  ggplot(aes(x=rfm_sq,y=n))+geom_bar(stat='identity')+geom_hline(aes(yintercept=breakeven_response_rate))+ coord_flip()+theme(axis.text.y = element_text(face="bold", color="black", size=5))
plot(plot_iq)
plot(plot_sq)
```

Question10:
When I compare rfm_iq and rfm_sq, most of the time(63%) they are the same but they are not totally the same.On the tail and head of the whole dataset,which means the most loyal customer and the least loyal customer,iq and sq method have the same result.And in the middle of the data,sq has a better evaluation.
Rfm_iq and Rfm_sq yield different RFM index for customers because there are different algorithm.Based on the calculation result,sq method has a higher ROME rate which is in accordance with the result professor given in class.If we think logically,sq method will not lead to a higher profit but it will indeed lead to a higher ROME rate.Sq method is an improvement of iq method and we can consider it a three iteration of iq method.It will lead to a more precise result and sometime the target customer will become fewer than iq method but sq method will indeed more accurate.

```{r}
#question 11
perf_calc2 <- function(data,column_name){
  sq_data<- data%>%
  filter(buyer == 1)%>%
  group_by_at(column_name)%>%
  summarize(size = mean(ordersize))
  sq_data3<- data %>%
  group_by_at(column_name)%>%
  summarize(rate=mean(buyer),n=n())%>%
  right_join(sq_data,by = column_name)%>%
  mutate(breakeven_response_rate = 1.6/(size*0.5))%>%
  mutate(choose_test2 = breakeven_response_rate< rate)%>%
  filter(choose_test2 == TRUE)
  data <- data %>%
  mutate(choose_test3 = data[[column_name]]   %in% sq_data3[[column_name]]  )
  perc_choose_sq3 <- mean(data$choose_test3)
  number_choose_sq3 <- perc_choose_sq3 *250902
  dat_sq3 <- filter(data,choose_test3==TRUE)
  rep_rate_sq3<-mean(dat_sq3$buyer== 1)
  nr_resp_sq3 <-number_choose_sq3*rep_rate_sq3
  cost_sq3<-1.6*number_choose_sq3
  profit_sq3<-amount_spent*0.5*nr_resp_sq3-cost_sq3
  ROME_sq3 <-profit_sq3/cost_sq3
  return(c(profit_sq3,ROME_sq3))
}

c<-perf_calc2(tuango,'rfm_sq')
c
profit_sq3 <-c[1]
ROME_sq3 <- c[2]

```
Question11 profit is 449380 and ROME is 1.9766

```{r}
perf_calc3 <- function(data,column_name){
  sq_data<- data%>%
  filter(buyer == 1)%>%
  group_by_at(column_name)%>%
  summarize(size = mean(ordersize))
  sq_data3<- data %>%
  group_by_at(column_name)%>%
  summarize(rate=mean(buyer)-1.64*seprop(buyer),n=n())%>%
  right_join(sq_data,by = column_name)%>%
  mutate(breakeven_response_rate = 1.6/(size*0.5))%>%
  mutate(choose_test2 = breakeven_response_rate< rate)%>%
  filter(choose_test2 == TRUE)
  data <- data %>%
  mutate(choose_test3 = data[[column_name]]   %in% sq_data3[[column_name]]  )
  perc_choose_sq3 <- mean(data$choose_test3)
  number_choose_sq3 <- perc_choose_sq3 *250902
  dat_sq3 <- filter(data,choose_test3==TRUE)
  rep_rate_sq3<-mean(dat_sq3$buyer== 1)
  nr_resp_sq3 <-number_choose_sq3*rep_rate_sq3
  cost_sq3<-1.6*number_choose_sq3
  profit_sq3<-amount_spent*0.5*nr_resp_sq3-cost_sq3
  ROME_sq3 <-profit_sq3/cost_sq3
  return(c(profit_sq3,ROME_sq3))
}
d<- perf_calc3(tuango,'rfm_iq')
e<-perf_calc3(tuango,'rfm_sq')
d
e
profit_iq2<-d[1]
ROME_iq2<-d[2]
profit_sq2<-e[1]
ROME_sq2<-e[2]
```

Question12
Profit of iq is 366891.49386 ROME of iq is 3.185
Profit of sq is 403526.238628 ROME of sq is 3.011

Method 12 has the best ROME rate which means it is more effective.When we try to solve the standard error, when improve the ROME rate sufficiently.Even though the profit become less ,the cost we need to pay is much smaller.



```{r}
library(dplyr)
bar_profit <- data.frame(name=c('iq_9','sq_9','sq_11','iq_12','sq_12'),profit=c(profit_iq,profit_sq,profit_sq3,profit_iq2,profit_sq2)) %>%
  ggplot(aes(x=name,y=profit))+geom_bar(stat = 'identity')+coord_cartesian(ylim=c(300000,500000))
bar_ROME <- data.frame(name=c('iq_9','sq_9','sq_11','iq_12','sq_12'),ROME=c(ROME_iq,ROME_sq,ROME_sq3,ROME_iq2,ROME_sq2)) %>%
  ggplot(aes(x=name,y=ROME))+geom_bar(stat = 'identity')+coord_cartesian(ylim=c(1.5,3.5))
bar_profit
bar_ROME  
```



```{r}
#useless
perf_calc5 <- function(data,column_name){
data_new<- data%>%
  filter(buyer == 1)%>%
  group_by_at(column_name)%>%
  summarize(size = mean(ordersize))
data_new2<- data %>%
  group_by_at(column_name)%>%
  summarize(rate=mean(buyer),n=n())%>%
  right_join(data_new,by = column_name)%>%
  mutate(choose = 1.6/(size*0.5)<rate)%>%
  filter(choose == TRUE)
data <- data %>%
  mutate(choose_test3 = data[[column_name]]   %in% data_new2[[column_name]]  )
  perc_choose_sq3 <- mean(data$choose_test3)
  number_choose_sq3 <- perc_choose_sq3 *250902
  dat_sq3 <- filter(data,choose_test3==TRUE)
  rep_rate_sq3<-mean(dat_sq3$buyer== 1)
  nr_resp_sq3 <-number_choose_sq3*rep_rate_sq3
  cost_sq3<-1.6*number_choose_sq3
  profit_sq3<-amount_spent*0.5*nr_resp_sq3-cost_sq3
  ROME_sq3 <-profit_sq3/cost_sq3
  return(c(profit_sq3,ROME_sq3))
}



```

